---
title: "ESM211_HW1"
author: "Robert Saldivar"
date: "January 9, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The population could be patchily distruted for the following reasons:
  a. The patches could be sites of a limiting resource  that the species needs to survive. In this situation I would expect high density patches as all the individuals would gather around the limiting resource.
  b.
  c.

```{r, include = FALSE}
#Loading the packages that will be needed and the data.
library(tidyverse) #Loading in the tidyverse package


```


**Eureka Dune Grass**
2.
```{r, message = FALSE}
Swallenia <- read_csv("Swallenia.csv") #this reads in the swallenia data

#Some initial data exploration
swallenia_summary <- Swallenia %>%
  summarize(
    count_2009_mean <- mean(count_2009),
    count_2009_sd <- sd(count_2009),
    count_2010_mean <- mean(count_2010),
    count_2010_sd <- sd(count_2010)
  )

Swallenia_ttest <- t.test(Swallenia$count_2009, Swallenia$count_2010, conf.level = 0.95) #this conducts a t test at a 95% confidence interval to compare the abundance of Swallenia in 2009 to the abundance of Swallenia in 2010.


Swallenia_ttest #Calls the results of the t test for viewing


```

The confidence level was chosen to be 95% because that is the most commonly used confidence level used for significance.

Based on the t-test analysis there is 

3.
```{r}
#Running a paired t test

Swallenia_Paired_Test <- t.test(Swallenia$count_2009, Swallenia$count_2010, conf.level = 0.95, paired= TRUE) #Running the analysis on the change in Swallenia as a paired t test

Swallenia_Paired_Test #Calling the paired t test results to view


```


Based on the analysis of a paired t test there is

4.
The analysis that is more appropriate to use is


5.


**Yellowstone Grizzly Bears**


```{r}
#Getting the grizzly data ready to be analyzed

grizzly <- read_csv("grizzlydata.csv") #this reads in the grizzly data

grizzly_59_68 <- grizzly %>%
  filter(Year <= 1968) # this is filtering the data so that only the population before 1969 is available

grizzly_69_78 <- grizzly %>%
  filter(Year >= 1969, Year <= 1978) #This is a filtering the data so that only the population between 1969 and 1978 is available

grizzly_79 <- grizzly %>%
  filter(Year >= 1979) #This is filtering the data so that only the population after 1979 is available

grizzly_graph <- ggplot(grizzly, aes(x=Year, y=N)) +
  geom_line()

grizzly_graph


```

6.

```{r}
#creating a graph and analyzing the statistics between of the grizzly population between 1959 and 1968
grizzly_graph_59_68 <- ggplot(grizzly_59_68, aes(x=Year, y=N)) +
  geom_line() #This is creating a line graph of the grizzly population between 1959 and 1968

grizzly_59_68_ttest <- t.test(grizzly_59_68$N)


grizzly_graph_59_68
grizzly_59_68_ttest

```


7. 
```{r}
grizzly_graph_69_78 <- ggplot(grizzly_69_78, aes(x=Year, y=N)) + 
  geom_line()

grizzly_68_78_ttest <- t.test(grizzly_69_78$N)


grizzly_graph_69_78
grizzly_68_78_ttest
```


8.
```{r}
grizzly_graph_79 <- ggplot(grizzly_79, aes(x=Year, y=N)) +
  geom_line()

grizzly_79_ttest <- t.test(grizzly_79$N)

grizzly_graph_79
grizzly_79_ttest
```


9.